---
output:
  word_document: default
  html_document: default
---
#Libraries and Packages
library(caret) #library for classification and regression training
library(rpart) #library for data partition and preprocessing
library(rpart.plot) #Data visualization for decision trees
library(rminer) #Data mining & classification methods
library(nnet) #Neural Net
library(ggplot2) #Visualization
library(ggthemes)
library(Amelia) #For missing data
library(caTools) #Performance of movind window stats
library(dummies) #convert factors to dummy variables
library(xlsx) # Export Excel file
library(dplyr) # Package for working with Data Frames
library(corrplot) # Display correlation plots
library("FactoMineR") # Perfrom exploratory analysis on multivariate data
library("factoextra") #Extract and visualize multivariate data
library(MASS)
library(car)
library("pROC") #Used for generating ROC curves
library(emmeans) #Estimate Least Square Means
library(tidyverse)
library(jtools) # summary, standardize, and plot functions for models
library(ggstance) #A 'ggplot2' extension that flips components: horizontal versions of 'Stats' and 'Geoms', & vertical versions of 'Positions'
#library(train) #used for various model building


#set working directory
setwd(file.path("C:/Users/Dominic/Documents/R/WGU"))

# Read from local file
data.raw <- read.csv("customer_data.csv", header = TRUE)

#Characterize the data
str(data.raw)
summary(data.raw)


### DATA CLEANING #################################################################

#Capture missing value data w/ missmap 
```{r}
missmap(data.raw,
        col = c("Red", "Green"),
        legend = TRUE,
        x.cex = 0.8,
        y.cex = 0.8,
        main = "Missing Customer Data",
        rank.order = FALSE,
        y.labels = c(seq(1,7044, by=500)),
        y.at = c(seq(1,7044,by=500)))
```

#Locate missing values in a dataframe
```{r}
sapply(data.raw, function(x) sum(is.na(x))) # all 11 in TotalCharges
```

#Returns rows w/ missing TotalCharges: due to 0 tenure
```{r}
data.raw[is.na(data.raw$TotalCharges),c(1,6, 20)]
```

#Check for other 0 tenure observations
library(dplyr)
data.raw %>%
  filter(tenure == 0) %>%
  summarise(n()) #returns 11: no other observarions with 0 tenure

#Remove 11 observations w/ 0 tenure
data.prep <- data.raw[complete.cases(data.raw),]
dim(data.prep) #7032

#Use propercase for Gender/Tenure variables
data.prep <- data.prep %>%
  rename(Gender=gender, Tenure=tenure)

#Convert senior citizen status to Y/N for readability: as.factor formats to factor as needed for analysis
data.prep$SeniorCitizen <- as.factor(ifelse(data.prep$SeniorCitizen == 0, "No", "Yes"))
```{r}
data.prep$SeniorCitizen[c(1:100,1)]
```

### CORRELATION ANALYSIS
# TotalCharges is highly correlated with both Tenure and MonthlyCharges
numeric.vars <- sapply(data.prep, is.numeric)
corr.matrix <- cor(data.prep[,numeric.vars])
corr.matrix

# View correlation as # table chart
```{r}
corrplot(corr.matrix, method="number",)
```

#Remove Customer ID: adds no value / Remove TotalCharges: highly correlated w/ MonthlyCharges & Tenure
data.prep <- data.prep[,-c(1,20)]

# Verify correlation was addressed
numeric.vars <- sapply(data.prep, is.numeric)
corr.matrix <- cor(data.prep[,numeric.vars])
```{r}
corrplot(corr.matrix, main="\n Correlation Plot", method="number")
```


#Replace "No internet service" and "No phone service" w/ "No" as these values all require internet/phone
str(data.prep) #shows where several variables w/ 3 levels would be more efficent w/ 2 levels

data.clean <- data.prep %>%
  mutate_at(vars(OnlineSecurity,OnlineBackup,DeviceProtection,TechSupport,StreamingMovies,StreamingTV), 
            funs(recode_factor(.,'No internet service'="No"))) %>%
              mutate_at(vars(MultipleLines),
                        funs(recode_factor(.,'No phone service'="No")))

#Verify predictors stored as factors
```{r}
str(data.clean)
```

### Export cleaned data to Excel ###
write.xlsx(data.clean, file = "data_clean.xlsx")



### UNIVARIATE ANALYSIS ###########################################################

# Check for outliers
```{r}
boxplot(data.clean$Tenure,ylab="Months", main="Customer Tenure Data")
```

```{r}
boxplot(data.clean$MonthlyCharges, ylab="Monthly Charges", main="Customer Monthly Charge Data")
```


#Summary of Tenure 
```{r}
summary(data.clean$Tenure)
```

#Summary of Monthly Charge
```{r}
summary(data.clean$MonthlyCharges)
```

### UNIVARIATE VISUALIZATIONS 

#Current Churn Data: Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$Churn)) +
  geom_bar(fill=c("Green", "Red"))+
  labs(title = "Customer Churn Data", x="Churn?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5)) 
```

# Capture percentage of churners
```{r}
churnrate <- table(data.clean$Churn) / nrow(data.clean)
churnrate
```

#Current Demographic Data: Male vs Female (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$Gender)) +
  geom_bar(fill=c("Pink", "Blue"))+
  labs(title = "Customers by Gender", x="Gender", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5)) 
```

#Current Demographic Data: Senior Citizen - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$SeniorCitizen)) +
  geom_bar(fill=c("Green", "Gray"))+
  labs(title = "Customers by Senior Citizen Status", x="Senior Citizen?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5)) 
```

#Current Demographic Data: Partner - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$Partner)) +
  geom_bar(fill=c("Gray", "Purple"))+
  labs(title = "Customers by Relationship Status", x="Partner vs No Partner", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Dependents - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$Partner)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Dependent Status", x="Dependents?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Customer Data by Age of Account: 0-72 Months; 6-month bins; bimodal (Univaritate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$Tenure)) +
  geom_histogram(fill="bisque", colour = "Black", alpha=0.5, bins = 72) +
  scale_x_continuous() +
  labs(title = "Customers by Age of Account", x="Months", y="# of Customers") +
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Phone Service - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$PhoneService)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Phone Service Status", x="Phone?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```


#Current Demographic Data: Multiple Lines - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$MultipleLines)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Line Status", x="Multiple Lines?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Internet Service - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$InternetService)) +
  geom_bar(fill=c("Orange", "Blue", "Grey"))+
  labs(title = "Customers by Internet Service Status", x="Internet Type", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Online Security - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$OnlineSecurity)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Online Security Status", x="Online Security?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Online Backup - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$OnlineBackup)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Online Backup Status", x="Online Backup?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Device Protection - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$DeviceProtection)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Device Protection Status", x="Device Protection?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Tech Support - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$TechSupport)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Tech Support Status", x="Tech Support?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Streaming TV - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$StreamingTV)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Streaming TV Status", x="Streaming TV?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Streaming Movies - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$StreamingMovies)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Streaming Movies Status", x="Streaming Movies?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Customer Data by Contract Type (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$Contract)) +
  geom_bar()+
  labs(title = "Customers by Contract Type", x="Contract Type", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Paperless Billing - Yes or No (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$PaperlessBilling)) +
  geom_bar(fill=c("Gray", "Blue"))+
  labs(title = "Customers by Paperless Billing Status", x="Paperless Billing?", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Current Demographic Data: Payment Method (Univariate Analysis)
```{r}
ggplot(data=data.clean, aes(x = data.clean$PaymentMethod)) +
  geom_bar(fill=c("Blue", "Green", "Orange", "Red"))+
  labs(title = "Customers by Payment Type", x="Payment Method", y="# of Customers") +
  geom_text(stat = 'count', aes(label=..count.., vjust=-0.5))+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

#Customer Data by Monthly Charge in USD (Univariate Analysis); bimodal
```{r}
ggplot(data=data.clean, aes(x=data.clean$MonthlyCharges)) +
  geom_histogram(fill="bisque", colour = "Black", alpha=0.5, binwidth = 10) +
  scale_x_continuous() +
  labs(title = "Customers by Monthly Bill", x="Monthly Charge Breakout", y="# of Customers") +
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```



### BIVARIATE ANALYSIS#############################################################
# All vars not compared with churn.  Tableau was used as primary bivariate analysis tool

# Churn vs Gender
```{r}
ggplot(data.clean,aes(x=Gender, fill = Churn))+
  geom_bar(position = "stack") +
  labs(title = "Churn vs Gender", y="Count", x="Proportion of Churners by Gender")+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5)) 
```

# Churn vs Tenure
```{r}
ggplot(data.clean,aes(x=Tenure, fill = Churn))+
  geom_bar(position = "stack") +
  labs(title = "Churn vs Tenure", y="Count", x="Proportion of Churners by Tenure")+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5)) 
```

# Churn vs Senior Citizen
```{r}
ggplot(data.clean,aes(x=SeniorCitizen, fill = Churn))+
  geom_bar(position = "stack") +
  labs(title = "Churn vs Senior Citizen", y="Count", x="Proportion of Churners by Senior Citizen Status")+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

# Bin Monthly Charges for better visualization
```{r}
data.binned <- data.clean
data.binned$MonthlyCharges <- as.factor(car::recode(data.clean$MonthlyCharges,
                                                 "1:40 = '0 - 40: Low Charge';
                                                 41:80 = '40 - 80: Medium Charge';
                                                 else = 'High Charge'"))

# Churn vs Montly Charge
ggplot(data.binned,aes(x=MonthlyCharges, fill = Churn))+
  geom_bar(position = "stack") +
  labs(title = "Churn vs Monthly Charge", y="Count", x="Proportion of Churners by Monthly Charges")+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5)) 
```

#Churn vs Payment Method
```{r}
ggplot(data.clean,aes(x=PaymentMethod, fill = Churn))+
  geom_bar(position = "stack") +
  labs(title = "Churn vs Payment Method", y="Count", x="Proportion of Churners by Payment Method")+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5))
```

# Churn vs Contract Length/Type
```{r}
ggplot(data.clean,aes(x=Contract, fill = Churn))+
  geom_bar(position = "stack") +
  labs(title = "Churn vs Contract Type", y="Count", x="Proportion of Churners by Contract Length")+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5)) 
```

# Churn vs Internet Service
```{r}
ggplot(data.clean,aes(x=InternetService, fill = Churn))+
  geom_bar(position = "stack") +
  labs(title = "Churn vs Internet Service", y="Count", x="Proportion of Churners by Internet Service")+
  theme(axis.title.y = element_text(margin = margin(t=0,r=10,b=0,l=0)), 
        axis.title.x = element_text(margin = margin(t=10,r=0,b=0,l=0)),
        plot.title = element_text(hjust = 0.5, vjust = 1.5)) 
```

# View Tenure across other suspected important variables as boxplot
```{r}
boxplot(Tenure~Contract, data = data.clean, main="Customer Tenure by Contract Type")
```

```{r}
boxplot(Tenure~PaymentMethod, data = data.clean, main="Customer Tenure by Payment Type")
```

```{r}
boxplot(Tenure~Churn, data = data.clean, main="Customer Tenure by Churn")
```

#Boxplot of Monthly Charges by Churn
```{r}
boxplot(MonthlyCharges~Churn, data = data.clean, main="Monthly Charge by Churn")


```


### DESCRIPTIVE ANALYSIS - MCA (QUALITATIVE DATA)##################################
# Reference: https://datascienceplus.com/using-mca-and-variable-clustering-in-r-for-insights-in-customer-attrition/
##################################################################################-

data.MCA <- data.clean

#Convert quantitative inputs to factors for MCA analysis
data.MCA$Tenure <- as.factor(car::recode(data.clean$Tenure, 
                                                "1:24 = 'ShortTenure'; 
                                                25:48 = 'MediumTenure'; 
                                                else = 'LongTenure'"))

data.MCA$MonthlyCharges <- as.factor(car::recode(data.clean$MonthlyCharges, 
                                                 "1:40 = 'LowCharge';
                                                 41:80 = 'MediumCharge';
                                                 else = 'HighCharge'"))
mca(data.MCA)
res.mca <- MCA(data.MCA, ncp = 5)

# Calculate eigenvalue, percentage of variance, cumulative percentage of variance 
eig.mca <- res.mca$eig
eig.mca

# Scree plot w/ eigenvalues
```{r}
fviz_screeplot(res.mca, choice="eigenvalue", addlabels=TRUE, title = "MCA Scree Plot: Eignevalue") #graph actual eignevalues
```

```{r}
fviz_screeplot(res.mca, choice="variance", addlabels=TRUE, title = "MCA Scree Plot: Variance") #graph percentage
```


# Variable contribution to dimensions (vs individual)...
# Reference line corresponds to the expected value if the contributions where uniform
# Contribution to the first dimension...
```{r}
fviz_contrib(res.mca, "var", axes = 1,
              fill = "lightblue", color = "black") +
              theme_minimal() +
              theme(axis.text.x = element_text(angle=90))
```

# Contribution to the second dimension...
```{r}
fviz_contrib(res.mca, "var", axes = 2,
              fill = "lightblue", color = "black") +
              theme_minimal() +
              theme(axis.text.x = element_text(angle=90))
```
# Contribution to the third dimension...
```{r}
fviz_contrib(res.mca, "var", axes = 3,
              fill = "lightblue", color = "black") +
              theme_minimal() +
              theme(axis.text.x = element_text(angle=90))
```


# Display variables: Correlation plot between variables along principal dimensions
```{r}
fviz_mca_var(res.mca, 
             choice = "var", 
             title = "Variables Correlation Along Principal Dimensions", 
             col.var = "blue",
             repel = TRUE,
             ggtheme = theme_minimal())
```

# Display variables by variable factor levels
```{r}

fviz_mca_var(res.mca, choice = "var.cat", 
             title = "Variables Category Correlation Along Principal Dimensions",
             col.var = "black",
             repel = TRUE,
             ggtheme = theme_minimal())
```



### DESCRIPTIVE ANALYSIS - FAMD (MIXED DATA) ######################################
# Reference: http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/115-famd-factor-analysis-of-mixed-data-in-r-essentials/#computation
##################################################################################-

#FAMD - resource intense; only use on full dataset after testing all other code!!!
#res.famd <- FAMD(data.clean[1:100,], ncp = 5)
res.famd <- FAMD(data.clean, ncp = 5)
res.famd

# Calculate eigenvalue, percentage of variance, cumulative percentage of variance 
eig.val <- res.famd$eig
eig.val

#Scree plot of eignevalues
```{r}

fviz_screeplot(res.famd, 
               choice="eigenvalue", 
               addlabel = TRUE, 
               barfill = "lightblue") 
```
# Screeplot of percentage of variance explained by each dimension
```{r}
fviz_screeplot(res.famd, 
               choice="variance", 
               addlabel = TRUE, 
               barfill = "lightblue")  
```
# Variable contribution to dimensions...
# Reference line corresponds to the expected value if the contribution where uniform
# Contribution to the first dimension
```{r}
fviz_contrib(res.famd, "var", axes = 1,
              fill = "lightblue", color = "black") +
              theme_minimal() +
              theme(axis.text.x = element_text(angle=90))
```
# Contribution to the second dimension...
```{r}
fviz_contrib(res.famd, "var", axes = 2,
              fill = "lightblue", color = "black") +
              theme_minimal() +
              theme(axis.text.x = element_text(angle=90))
```

# Contribution to the third dimension...
```{r}
fviz_contrib(res.famd, "var", axes = 3,
              fill = "lightblue", color = "black") +
              theme_minimal() +
              theme(axis.text.x = element_text(angle=90))
```

# Plot variable correlations along principal dimensions
```{r}
fviz_famd_var(res.famd, 
              choice = "var", 
              title = "Variable Correlation Along Principal Dimensions 1 & 2",
              repel = TRUE,
              ggtheme = theme_minimal())
```



### PREDICTIVE MODEL: LOGISTIC REGRESSION#################################################################
# Reference: https://rpubs.com/aelhabr/logistic-regression-tutorial
### -------------------------------- ###

#Set random seed for reproducing results
set.seed(2)

# Data Partition 75/25 Split
inTrain <- createDataPartition(y=data.clean$Churn, p = 0.75, list = FALSE) #creates vector sampling x% of rows
clean.train <- data.clean[inTrain,] #assigns x% of rows as randomly selected to dataset
clean.test <- data.clean[-inTrain,] #assigns not selected rows from random sample vector to dataset


# LOGISTIC REGRESSION MODEL w/ ALL inputs
glm_FULL <- glm(Churn ~ ., data=clean.train, family = "binomial")
summary(glm_FULL)

# STEPWISE MODEL
# Drops InternetService, Partner, StreamingMovies, StreamingTV, MultipleLines
glm_STEP <- stepAIC(glm_FULL, Churn ~ ., direction = "both", trace = FALSE)
summary(glm_STEP)

#View impact to AIC at each step of dropping/adding variables
```{r}
glm_STEP$anova
```

#INTERACTIONS (Based on stepwise model)
glm_INTERACTIONS <- stepAIC(glm_STEP, Churn ~ .^2, direction = "both", trace = FALSE)
summary(glm_INTERACTIONS)

#View impact at each step dropping/adding variables/interactions
```{r}
glm_INTERACTIONS$anova
```



### EVALUATE PREDICTIVE CAPABILITY #################
# Reference: https://github.com/susanli2016/Data-Analysis-with-R/blob/master/customer_churn.Rmd
###################################################-

#Run predictions against TRAINING data set & convert probabilities to classifications
trng_predictions <- ifelse(predict(glm_FULL, type="response") > 0.5, "Yes", "No")
trng_predictions_STEP <- ifelse(predict(glm_STEP, type="response") > 0.5, "Yes", "No")
trng_predictions_INTERACTIONS <- ifelse(predict(glm_INTERACTIONS, type="response") > 0.5, "Yes", "No")

#Make predictions against TEST set
test_predictions <- ifelse(predict(glm_FULL, newdata=clean.test,type="response") > 0.5, "Yes", "No")
test_predictions_STEP <- ifelse(predict(glm_STEP, newdata=clean.test,type="response") > 0.5, "Yes", "No")
test_predictions_INTERACTIONS <- ifelse(predict(glm_INTERACTIONS, newdata=clean.test,type="response") > 0.5, "Yes", "No")

# Generate Confusion Matrix for TRAINING data
trng_table <- table(predicted = trng_predictions, actual = clean.train$Churn)
trng_table_STEP <- table(predicted = trng_predictions_STEP, actual = clean.train$Churn)
trng_table_INTERACTIONS <- table(predicted = trng_predictions_INTERACTIONS, actual = clean.train$Churn)

print("Confusion Matrix for Training Data"); trng_table
print("Confusion Matrix for Training Data: STEP"); trng_table_STEP
print("Confusion Matrix for Training Data: INTERACTIONS"); trng_table_INTERACTIONS

# Generate Confusion Matrix for TEST data
```{r}
#Full model
test_table <- table(predicted = test_predictions, actual = clean.test$Churn)
test_table

```

```{r}
#Stepwise model
test_table_STEP <- table(predicted = test_predictions_STEP, actual = clean.test$Churn)
test_table_STEP

```

```{r}
#Interaction model
test_table_INTERACTIONS <- table(predicted = test_predictions_INTERACTIONS, actual = clean.test$Churn)
test_table_INTERACTIONS

```


# Create function to calculate classification error rate
calc_class_error <- function(actual,predicted) {
  mean(actual != predicted)}

# Calculate classification error rate for TRAINING data
calc_class_error(actual = clean.train$Churn, predicted = trng_predictions)
calc_class_error(actual = clean.train$Churn, predicted = trng_predictions_STEP)
calc_class_error(actual = clean.train$Churn, predicted = trng_predictions_INTERACTIONS)

# Calculate Classification Error Rate for TEST data
```{r}
error_rate_FULL <- calc_class_error(actual = clean.test$Churn, predicted = test_predictions)
error_rate_FULL
```

```{r}
error_rate_STEP <- calc_class_error(actual = clean.test$Churn, predicted = test_predictions_STEP)
error_rate_STEP
```

```{r}
error_rate_INTERACTIONS <- calc_class_error(actual = clean.test$Churn, predicted = test_predictions_INTERACTIONS)
error_rate_INTERACTIONS
```

# Accuracy of TRAINING predictions 
# Returns accuracy, confusion matrix, 95% CI, Sensitivity, Specificity and more...
confusionMatrix(trng_table, positive = "Yes")
confusionMatrix(trng_table_STEP, positive = "Yes")
confusionMatrix(trng_table_INTERACTIONS, positive = "Yes")

#Accuracy of TEST predictions
```{r}
CM_FULL <- confusionMatrix(test_table, positive = "Yes")
CM_FULL[["overall"]][["Accuracy"]]
```

```{r}
CM_STEP <- confusionMatrix(test_table_STEP, positive = "Yes")
CM_STEP[["overall"]][["Accuracy"]]
```

```{r}
CM_INTERACTIONS <- confusionMatrix(test_table_INTERACTIONS, positive = "Yes")
CM_INTERACTIONS[["overall"]][["Accuracy"]]
```


#ROC for TRAINING data (Sensitivity/Specificity)
trng_prob <- predict(glm_FULL, newdata=clean.train, type="response")
trng_ROC <- roc(clean.train$Churn ~ trng_prob, plot=TRUE, print.auc=TRUE)

trng_prob_STEP <- predict(glm_STEP, newdata=clean.train, type="response")
trng_ROC_STEP <- roc(clean.train$Churn ~ trng_prob_STEP, plot=TRUE, print.auc=TRUE)

trng_prob_INTERACTIONS <- predict(glm_INTERACTIONS, newdata=clean.train, type="response")
trng_ROC_INTERACTIONS <- roc(clean.train$Churn ~ trng_prob_INTERACTIONS, plot=TRUE, print.auc=TRUE)


#ROC/AUC for TEST data
test_prob <- predict(glm_FULL, newdata=clean.test, type="response")
test_ROC <- roc(clean.test$Churn ~ test_prob, plot=TRUE, print.auc=TRUE)

test_prob_STEP <- predict(glm_STEP, newdata=clean.test, type="response")
test_ROC_STEP <- roc(clean.test$Churn ~ test_prob_STEP, plot=TRUE, print.auc=TRUE)

test_prob_INTERACTIONS <- predict(glm_INTERACTIONS, newdata=clean.test, type="response")
test_ROC_INTERACTIONS <- roc(clean.test$Churn ~ test_prob_INTERACTIONS, plot=TRUE, print.auc=TRUE)


### LOGISTIC REGRESSION FINAL MODEL SELECTION/COMPARISON ####################
# Reference: https://cran.r-project.org/web/packages/jtools/vignettes/summ.html#plot_summs_and_plot_coefs
# Goodness of fit measures: χ², AIC, ROC, Accuracy, Sensitivity, Specificity
##########################################################################-

#Summary of model goodness of fit measures: χ², R² (Cragg-Uhler), R² (McFadden), AIC, BIC
FULL_summ <- summ(glm_FULL, scale = TRUE, confint = TRUE) #scale standardizes the predictor for comparison between variables
STEP_summ <- summ(glm_STEP, scale = TRUE, confint = TRUE) #scale standardizes the predictor for comparison between variables
INTERACTIONS_summ <- summ(glm_INTERACTIONS, scale = TRUE, confint = TRUE) #scale standardizes the predictor for comparison between variables

#ROC/AUC
test_ROC <- roc(clean.test$Churn ~ test_prob, plot=TRUE, print.auc=TRUE)
test_ROC_STEP <- roc(clean.test$Churn ~ test_prob_STEP, plot=TRUE, print.auc=TRUE)
test_ROC_INTERACTIONS <- roc(clean.test$Churn ~ test_prob_INTERACTIONS, plot=TRUE, print.auc=TRUE)

#Accuracy: best predictor overall
```{r}
Accuracy_FULL <- CM_FULL$overall[["Accuracy"]]
Accuracy_FULL
```

```{r}
Accuracy_STEP <- CM_STEP$overall[["Accuracy"]]
Accuracy_STEP
```

```{r}
Accuracy_INTERACTIONS <- CM_INTERACTIONS$overall[["Accuracy"]]
Accuracy_INTERACTIONS
```

#Sensitivity: best @ identifying churners
```{r}
Sensitivity_FULL <- CM_FULL$byClass[["Sensitivity"]]
Sensitivity_FULL
```

```{r}
Sensitivity_STEP <- CM_STEP$byClass[["Sensitivity"]]
Sensitivity_STEP
```

```{r}
Sensitivity_INTERACTIONS <- CM_INTERACTIONS$byClass[["Sensitivity"]]
Sensitivity_INTERACTIONS
```


#Specificity: best @ identifying non-churners
```{r}
Specificity_FULL <- CM_FULL$byClass[["Specificity"]]
Specificity_FULL
```

```{r}
Specificity_STEP <- CM_STEP$byClass[["Specificity"]]
Specificity_STEP 
```

```{r}
Specificity_INTERACTIONS <- CM_INTERACTIONS$byClass[["Specificity"]]
Specificity_INTERACTIONS
```

#Confusion matrix plot
 fourfoldplot(test_table_STEP)
fourfoldplot(test_table_INTERACTIONS)


### INTERPRET LOGISTIC REGRESSION RESULTS #######################################
#Standardized coefficients w/ 95% confidence intervals, z-value, and p-value
```{r}
FULL_summ <- summ(glm_FULL, scale = TRUE, confint = TRUE)
FULL_summ
```


```{r}
#Standardized coefficients w/ 95% confidence intervals, z-value, and p-value
STEP_summ <- summ(glm_STEP, scale = TRUE, confint = TRUE)
STEP_summ
```


```{r}
INTERACTIONS_summ <- summ(glm_INTERACTIONS, scale = TRUE, confint = TRUE)
INTERACTIONS_summ
```

# Visualize the standardize estimates with confidence intervals
```{r}
plot_summs(STEP_summ)
```

```{r}
plot_summs(INTERACTIONS_summ)
```

# ODDS RATIO - Likelihood versus referece level or single unit increase is predictor
```{r}
odds_FULL <-  coef(glm_FULL) %>% exp() %>% round(2)
odds_FULL
```

```{r}
odds_STEP <-  coef(glm_STEP) %>% exp() %>% round(2)
odds_STEP
```


```{r}
odds_INTERACTIONS <-  coef(glm_INTERACTIONS) %>% exp() %>% round(2)
odds_INTERACTIONS
```



